---
title: "Exercise 4"
output: html_document
date: "2024-03-05"
---

```{r setup, include=FALSE}
library(kableExtra)
```

```{r, message=F}
library(dplyr)
library(quanteda) # includes functions to implement Lexicoder
library(quanteda.textmodels) # for estimating similarity and complexity measures
library(quanteda.textplots) #for visualizing text modelling results
```

## Importing data

```{r}
kaneko_dfm  <- readRDS(gzcon(url("https://github.com/cjbarrie/CTA-ED/blob/main/data/wordscaling/study1_kaneko.rds?raw=true")))

```

## Manipulate data in the same way as @kaneko_estimating_2021
This data is in the form a document-feature-matrix. Grouping them at the level of newspaper and removing infrequent words.

```{r}
table(docvars(kaneko_dfm, "Newspaper"))
## prepare the newspaper-level document-feature matrix
# compress the document-feature matrix at the newspaper level
kaneko_dfm_study1 <- dfm_group(kaneko_dfm, groups = Newspaper)
# remove words not used by two or more newspapers
kaneko_dfm_study1 <- dfm_trim(kaneko_dfm_study1, min_docfreq = 2, docfreq_type = "count")

## size of the document-feature matrix
dim(kaneko_dfm_study1)

```

## Exercises

1. Estimate a wordfish model for the @kaneko_estimating_2021 data
```{r}
#### estimate the Wordfish model ####
set.seed(123L)
dfm_kaneko_results<- textmodel_wordfish(kaneko_dfm_study1, 
                                             sparse = TRUE) #Specify the matrix in a sparse format
```

```{r}
#### Output results ####
summary(dfm_kaneko_results)
```

2. Visualize the results
```{r}
#We can then plot the estimates of the latent newspaper position.
textplot_scale1d(dfm_kaneko_results)
```

Most newspapers with high influence have high estimates. This can be seen from their position on the right side of the potential dimension. However, Asahi, which is considered a leading newspaper, has an estimated score of around -1.On the other hand, tabloids have lower estimated scores and are located on the left-hand side. This could mean that tabloids are perceived to be less influential or have a different level of influence compared to mainstream newspapers.

```{r}
#Plotting the word-level betas.
textplot_scale1d(dfm_kaneko_results, margin = "features")
```

```{r}

features <- dfm_kaneko_results[["features"]] #Extract the "features" column.

betas <- dfm_kaneko_results[["beta"]] #Extract the "beta" column.

feat_betas <- as.data.frame(cbind(features, betas)) #Combine the "features" and "betas" columns into a new dataframe.
feat_betas$betas <- as.numeric(feat_betas$betas) #Convert "betas" column to numeric.

feat_betas %>%
  arrange(desc(betas)) %>% #Arrange the rows in descending order based on the 'betas' column values.
  top_n(20) %>% #Select the top 20 rows with the highest 'betas' values.
  kbl() %>% #Convert the resulting dataframe into kable.
  kable_styling(bootstrap_options = "striped") #Use the Bootstrap style to add striped rows to the table.

```